Research

### 2025-10-01 research.qmd
Work in Progress
wise talk

## Working Papers

@@

-   Shaokang Yang, Idris Adjerid. *Friends over Feeds: How Social Smartphone Use Reduces Screen Time.* **Scheduled on INFORMS Annual Meeting (2:09 PM – 2:27 PM)**, Atlanta, GA, Oct 28, 2025.

>>>>

## Work in Progress

@@

-   Shaokang Yang, Idris Adjerid. *Smartphone Use, Social Support, and Sleep Health.* **Workshop on Information Systems and Economics (WISE)**, Nashville, TN, Dec 17--19, 2025.

-   Shaokang Yang, Idris Adjerid. *Friends over Feeds: How Social Smartphone Use Reduces Screen Time.* **Scheduled on INFORMS Annual Meeting **, Atlanta, GA, 2:09 PM – 2:27 PM, Oct 28, 2025.
